---
title: "Climate Resilience as a Housing Market Signal: Evidence from NOAA Storm Events and FEMA NRI Data"
author: "David Schaaf, Chris Clever, Neeraj Athani"
date: today
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    latex-engine: xelatex
    mainfont: "Times New Roman"
    sansfont: "Times New Roman"
    include-in-header:
      - text: |
          \usepackage{booktabs}
          \usepackage{float}
          \usepackage{amsmath}
          \usepackage{caption}
          \captionsetup{font=small,skip=3pt}
          \renewcommand{\topfraction}{0.9}
          \renewcommand{\bottomfraction}{0.8}
          \renewcommand{\textfraction}{0.1}
          \renewcommand{\floatpagefraction}{0.75}
          \setcounter{topnumber}{4}
          \setcounter{bottomnumber}{2}
          \setcounter{totalnumber}{6}
          \setlength{\textfloatsep}{8pt plus 2pt minus 2pt}
          \setlength{\intextsep}{6pt plus 2pt minus 2pt}
          \setlength{\floatsep}{8pt plus 2pt minus 2pt}
execute:
  echo: false
  warning: false
  message: false
  fig-pos: "htbp"
---

```{r setup}
#| results: hide
library(here)
library(kableExtra)
source(here::here("paper", "R", "eda_storms.R"))
source(here::here("paper", "R", "eda_zhvi.R"))
storm_eda <- run_storm_eda(here::here("paper", "output", "storms"))
zhvi_eda  <- run_zhvi_eda(here::here("paper", "output", "zhvi"))

# ---- Inline values ----
ss <- storm_eda$summary_stats
storms_raw <- storm_eda$storms

# Storm stats
n_county_months   <- format(ss$total_county_months, big.mark = ",")
n_events          <- format(ss$total_events, big.mark = ",")
n_episodes        <- format(ss$total_episodes, big.mark = ",")
n_storm_counties  <- format(ss$unique_counties, big.mark = ",")
storm_year_min    <- ss$year_min
storm_year_max    <- ss$year_max
total_damage_b    <- round(ss$total_damage / 1e9, 1)
median_damage     <- format(ss$median_damage, big.mark = ",")
pct_zero_damage   <- round(ss$pct_zero_damage * 100, 1)

# ZHVI stats
ts <- zhvi_eda$tier_summary
cs <- zhvi_eda$coverage_summary
n_zhvi_counties   <- format(max(ts$counties), big.mark = ",")
zhvi_date_min     <- format(min(cs$date_min), "%B %Y")
zhvi_date_max     <- format(max(cs$date_max), "%B %Y")
median_zhvi_bottom <- format(round(ts$median_zhvi[ts$tier == "Bottom"]), big.mark = ",")
median_zhvi_mid    <- format(round(ts$median_zhvi[ts$tier == "Mid"]), big.mark = ",")
median_zhvi_top    <- format(round(ts$median_zhvi[ts$tier == "Top"]), big.mark = ",")

# NRI stats
nri <- read_csv(here::here("data", "processed", "nri_panel_smooth.csv"),
                col_types = cols(stcofips = col_character()),
                show_col_types = FALSE)
n_nri_counties <- format(n_distinct(nri$stcofips), big.mark = ",")
nri_vintages   <- paste(sort(unique(nri$nri_vintage)), collapse = ", ")

# Hedonic
hed <- read_csv(here::here("data", "processed", "hedonic_dataset.csv"),
                show_col_types = FALSE)
n_hedonic_obs <- format(nrow(hed), big.mark = ",")
n_hedonic_counties <- format(n_distinct(hed$stcofips), big.mark = ",")

# Hedonic regression coefficients (computed in analysis/hedonic_xsec_zhvi_window_full.Rmd)
hed_inline <- readRDS(here::here("paper", "output", "regression", "hedonic_inline.rds"))
hed_income_coef <- hed_inline$hed_income_coef  # Spec A income elasticity
hed_sovi_coef_B <- hed_inline$hed_sovi_coef_B  # Spec B pooled SoVI coefficient
hed_sovi_coef_C <- hed_inline$hed_sovi_coef_C  # Spec C base SoVI coefficient
hed_eal_coef_E  <- hed_inline$hed_eal_coef_E   # Spec E (no income) log(EAL)
hed_resl_coef_E <- hed_inline$hed_resl_coef_E  # Spec E (no income) resilience
hed_sovi_coef_E <- hed_inline$hed_sovi_coef_E  # Spec E (no income) SoVI
hed_eal_min     <- hed_inline$hed_eal_min      # most negative log(EAL) across primary specs
hed_eal_max     <- hed_inline$hed_eal_max      # least negative log(EAL) across primary specs

# Capitalization benchmark: full pricing of modeled EAL as a 5% perpetuity
cap_units          <- 47000     # approx. housing units per county (US average)
cap_home_value     <- 368720    # Zillow US median home value
cap_county_eal     <- 14.8e6    # 2025 median county-total expected annual loss
cap_rate           <- 0.05      # perpetuity discount rate
cap_beta_benchmark <- round(-(cap_county_eal / cap_units / cap_home_value) / cap_rate, 3)
```
```{r setup-hedonic-legacy}
#| output: false
#| results: hide
#| message: false
source(here::here("paper", "R", "06_hedonic_plots.R"))
hed_legacy <- run_hedonic_plots_legacy(here::here("paper", "output", "hedonic"))
```
```{r setup-hedonic-rev}
#| output: false
#| results: hide
#| message: false
source(here::here("paper", "R", "06_hedonic_plots_rev.R"))
hed_rev <- run_hedonic_plots(
  df         = hed_inline$rucc_df,
  xsec_df    = hed_inline$xsec_df,
  models     = list(
    mC = hed_inline$mC, mE = hed_inline$mE, xs_B = hed_inline$xs_B,
    xs_2020 = hed_inline$xs_2020, xs_2021 = hed_inline$xs_2021,
    xs_2023 = hed_inline$xs_2023, xs_2025 = hed_inline$xs_2025
  ),
  output_dir = here::here("paper", "output", "hedonic")
)
```

# Abstract

FEMA's National Risk Index (NRI) is a composite metric created to determine the relative risk to 18 natural hazards for all areas of the United States. Using a two-part investigation, we first test whether real estate markets incorporate any of its risk or resilience components into pricing.
Next we stress test the hedonic findings with a natural experiment developed using NOAA storm data to understand how real estate markets respond post-hazard event and whether FEMA's expected annual loss, social vulnerability, and resilience scores correlate with heterogeneous outcomes.
This study does not find evidence of climate risk factors definitively incorporated into property pricing.


\newpage

# Introduction

## Motivation

Extreme weather events, including storms, floods, fires, tornadoes are becoming increasingly frequent, severe, and financially destabilizing. This volatility surged from 2020-2024, when inflation-adjusted annual costs for U.S. billion-dollar disasters averaged $149.3B, more than doubling the $64.8B average from 1980-2020 (Smith 2025). Despite insured losses reaching ~$100B annually, markets have been slow to adapt (Coren 2024, Parshley 2023).

U.S. housing markets are the single largest household asset class and a primary transmission channel for climate risk into the broader economy. The Congressional Budget Office (2023) estimates that homes with federally-backed mortgages face roughly $190 billion in cumulative expected flood damage under current climate conditions over a 30-year horizon, rising to $258 billion under projected 2050 conditions. The 2024 hurricane season made this exposure concrete: Hurricanes Helene and Milton affected counties containing 2.5 million GSE-backed single-family loans with combined unpaid principal balance exceeding $526 billion, according to FHFA's (2024) analysis of active September 2024 portfolios.

Whether housing markets correctly price the climate risks these capital and underwriting decisions reflect is contested. Gourevitch et al. (2023, Nature Climate Change) estimate that U.S. residential properties are overvalued by $121-$237 billion due to unpriced flood risk, with 83 percent of at-risk properties located outside FEMA's Special Flood Hazard Area boundaries. If markets are systematically mispricing physical risk, the question of whether they correctly value the offsetting factor, community resilience capacity, becomes equally consequential.

FEMA's Building Resilient Infrastructure and Communities program allocated $1 billion in the FY24-25 cycle that opened in March 2026, HUD's CDBG-MIT block grants have appropriated approximately $16 billion since 2018 for mitigation in disaster-affected areas, and the National Risk Index itself is built on the premise that ex-ante community resilience translates into measurable post-event outcomes. Yet the empirical record linking a county's resilience score to realized housing market performance after a storm is thin. 


## Prior Research

There is no federal requirement for climate risk disclosure in residential real estate transactions. This creates information asymmetry: buyers may not know the risk profile of a property or county. Baldauf (2020) found \~7% price discount in neighborhoods with more "climate believers", suggesting beliefs, not data, drive pricing. Bernstein (2019) documented similar discounts for homes exposed to sea-level rise.

Bakkensen (2017) estimated flood-prone waterfront properties were overvalued by 13% relative to non-flood zones - amenity value overrides risk. This contradicts the efficient markets hypothesis - if risk were priced correctly, flood-prone properties would trade at a discount, not a premium. The conflict between Baldauf/Bernstein (discount) and Bakkensen (premium) highlights that the market applies climate data erratically.

When risk is realized through extreme weather, delinquency rates rise and valuations fluctuate (Ma 2023, Wowk 2021). Büchler (2024) found commercial investors exposed to local heat shocks reactively rebalance - selling risky assets after the fact rather than pricing risk proactively. This reactive pattern suggests markets are not efficiently incorporating climate risk.

Prior work focuses on cross-sectional pricing (is risk priced at a point in time?) or post-hoc portfolio adjustment. This study examines the dynamic response. What happens to housing values in the months following a storm event, measured against a local counterfactual baseline? FEMA NRI provides a standardized measure of community resilience that we test as a moderator of post-storm recovery. We also examine whether baseline construction methodology affects the detectability of the effect.

# Data

We examine county level data for housing economic, severe weather event, and climate risk factors. Data spans six years from 2020-2025 in the 48 contiguous states. Alaska, Hawaii, and Puerto Rico are excluded because their geographic isolation differentiates those areas from the rest of the US States.

## Housing Market (Zillow ZHVI)
```{r fig-tier-dist, fig.cap="ZHVI distribution by market tier as of January 2023. Dashed lines indicate tier medians.", out.height="40%", fig.pos="H"}
knitr::include_graphics(here::here("paper", "output", "zhvi", "fig_tier_dist.pdf"))
```

We use the Zillow Home Value Index (ZHVI), a smoothed, seasonally-adjusted measure of typical monthly county-level home values for single-family residences and condominiums, derived from Zillow's home valuation model rather than transaction prices. We examine three market tiers: Bottom (0–33rd percentile), Mid (33rd–67th percentile), and Top (67th–100th percentile). Coverage spans approximately `r n_zhvi_counties` counties from `r zhvi_date_min` to `r zhvi_date_max`. As of January 2023, median ZHVI is \$`r median_zhvi_bottom` (Bottom), \$`r median_zhvi_mid` (Mid), and \$`r median_zhvi_top` (Top).

## Storm Events (NOAA)

We use the NOAA Storm Events Database covering 2020–2025, which records event-level storm occurrences including location, event type, duration, and property damage estimates. Storm events are organized into episodes; an episode is a single storm system that may produce multiple events across counties and time. We aggregate events to county-month observations. Event damage is defined as the sum of reported crop damage and property damage, and log1p transformed. Damage reporting is voluntary and inconsistently recorded.

Our sample covers `r n_county_months` county-month storm observations across `r n_storm_counties` unique counties from `r storm_year_min` to `r storm_year_max`, comprising `r n_events` individual events and `r n_episodes` episodes. Total reported damage is \$`r total_damage_b` billion, with a median of \$`r median_damage` per damaged county-month. `r pct_zero_damage`% of county-months report zero damage.

```{r fig-storm-heatmap, fig.cap="County-level storm exposure across the contiguous United States, 2020–2025.", out.height="40%"}
knitr::include_graphics(here::here("paper", "output", "storms", "fig_storm_heatmap.pdf"))
```

## Community Risk and Resilience (FEMA NRI)

We use the FEMA National Risk Index (NRI), a county-level composite of hazard exposure, social vulnerability, and community resilience published in four vintages (2020, 2021, 2023, 2025). The NRI covers `r n_nri_counties` counties. The NRI risk score is the product of Expected Annual Loss (EAL) and the Community Risk Factor (CRF), a ratio of Social Vulnerability Index (SoVI) to Community Resilience. Higher social vulnerability or lower resilience amplifies the base loss exposure. The CRF captures the community's capacity to absorb and recover from that loss.

$$\text{National Risk Index} = \text{Expected Annual Loss} \times \underbrace{\frac{\text{Social Vulnerability}}{\text{Community Resilience}}}_{\text{CRF}}$$

We match each storm observation to the most recent available NRI vintage using a forward-fill rule, and smooth NRI values on a monthly basis between vintage release dates to avoid discrete jumps at vintage boundaries.

FEMA revised its NRI methodology between the 2021 and 2023 releases, shifting from a relative index to an absolute dollar-based measure for Expected Annual Loss. 2020 and 2021 values were converted to the dollar-based measure following FEMA's documented methodology. This is a potential source of measurement discontinuity for events near that transition, distinct from the separate SoVI methodology break. Coastal county status is also derived from the NRI. A county is flagged coastal if any vintage reports positive coastal-flooding expected annual loss, which FEMA computes only for counties with Atlantic, Pacific, Gulf, or Great Lakes shoreline exposure.

## Supplementary Data

**American Community Survey (ACS).** County-level median household income from the 2019–2023 five-year ACS, accessed via `tidycensus`. Used in the hedonic regression and covariate balance analysis.

**County Adjacency File (Census Bureau).** County-to-county adjacency relationships used to construct the first ring (R1, adjacent) and second ring (R2) neighbor groups.

**Rural-Urban Continuum Codes (RUCC), USDA Economic Research Service.** 2023 vintage county-level urban/rural classification (9-point scale).

# Research Questions and Framework

## Questions

- What factors make up the raw Zillow ZHVI level for a county?

- Do housing markets reflect FEMA NRI risk metrics - expected loss, resilience, social vulnerability?

- Do storm events create measurable deviations in county-level housing values as measured by Zillow ZHVI relative to unaffected neighbors?

- Does FEMA NRI community resilience moderate the magnitude or duration of post-storm deviations?

- Does the effect differ across market segments (Bottom, Mid, Top tier ZHVI)?

- How sensitive are measured effects to baseline construction methodology?

## Methodological Framework

We use a two-phase approach to understand real estate market pricing relative to economic, demographic, and climate considerations.

We examine a descriptive cross-county hedonic regression of Zillow Home Value Index (ZHVI) on FEMA National Risk Index (NRI) components, controlling for ACS demographics and state and year-month fixed effects. The goal is to document whether higher climate risk and lower community resilience are associated with lower property values, conditional on observables.

Second, we test the hedonic model using a natural experiment with NOAA storm events. When a county is hit by a storm, we attempt to measure the market response relative to severity and damages. The neighboring counties that were unaffected by storm episodes serve as a counterfactual baseline though potential spillover effects must be considered. We estimate a full response curve to storm damages over the 9 months following a storm event.

Local Projections Difference-in-Differences (Dube, Girardi, Jordà, Taylor 2025) provides the framework for measuring dynamic treatment effects of discrete shocks. LP-DiD estimates a response curve across post-treatment periods, capturing both the magnitude and duration of a shock's effect. This is well-suited to storm events where the housing market response may be immediate, delayed, or cumulative.

We simplify the LP-DiD approach by pre-computing the Cumulative Impulse Response (CIR): the sum of monthly deviations across the post-storm window. CIR captures both severity and persistence in a single quantity. A county with a small but prolonged deviation scores similarly to one with a large but brief deviation. The tradeoff: collapsing the time dimension loses information about when effects materialize and how quickly they dissipate. We complement CIR with horizon-specific local projections that measure the temporal dynamics of the response to damages.

This approach requires a counterfactual: what would have happened absent the storm? Storm events are likely to have high rates of spillover across country boundaries that are not recorded in the NOAA data set. The frequency and geographic reach of spillover are unknown quantities. Directly adjacent neighboring counties would be most economically suitable for a counterfactual, but the spillover effect will also be highest for direct neighbors. We consider a baseline sensitivity analysis to understand the spillover of storm events.

# ZHVI Hedonic Analysis

This section estimates a cross-county hedonic model relating the Zillow Home Value Index to FEMA National Risk Index components and demographic controls. We report six specifications that progressively decompose the composite risk measure and assess the stability of each coefficient.

## County-level data

We need county-level controls that the NRI components don't already capture:

- Median household income - the largest non-NRI driver of housing value
- Coastal County Status - account for coastal amenity and/or risk (calculated as any county with any coastal flooding risk value in any year)
- Population density - controls for urban/rural market structure (population and land area from the NRI county fields)

Considered but left off due to overlap with community resilience and social vulnerability calculations:

- Share with bachelor's degree+ - human capital, picks up labor market quality
- Share owner-occupied - tenure mix shifts price dynamics
- Median age - lifecycle/retiree composition, related to migration patterns
- Median year structure built - housing stock vintage, captures durability

We deliberately do not pull poverty, vehicle access, household size, or disability share - those are inputs to the CDC SVI and would create multicollinearity with the Social Vulnerability.

## Hedonic Model Specifications

We run six specifications side by side. All use state + year-month fixed effects with standard errors clustered at the county level, and include log median income, log population density, and coastal status as controls.

- **Spec A (parsimonious, NRI's intended decomposition):** ZHVI \~ log(EAL) + log(CRF)
- **Spec B (separates resilience from social vulnerability):** ZHVI \~ log(EAL) + resilience + SoVI
- **Spec C (Spec B + regime interaction):** allow SoVI coefficient to differ pre/post March 2023
- **Spec D (Spec B - SoVI):** check if resilience multicollinearity with SoVI impacts coefficient
- **Spec E (Spec B - income):** check to see what income is absorbing from the NRI values
- **Spec F (Spec B + urban-rural continuum):** see if resilience coefficient changes when urban/ruralness accounted for

## Results

```{r tbl-hedonic}
#| results: 'asis'
#| tbl-cap: "Hedonic regression specifications A, B, C, D, E, F"
tex_lines <- readLines(here::here("paper", "output", "regression", "hedonic_regression.tex"))

begin_idx <- grep("\\begin{tabular}", tex_lines, fixed = TRUE)
end_idx   <- grep("\\end{tabular}",   tex_lines, fixed = TRUE)

tex_lines <- append(tex_lines, "\\resizebox{\\textwidth}{!}{", after = begin_idx - 1)
end_idx   <- end_idx + 1  # shift: one line was just inserted above it
tex_lines <- append(tex_lines, "}", after = end_idx)

writeLines(tex_lines)
```

The hedonic regression operates on a county-month panel of approximately `r n_hedonic_obs` observations. 

Specification A: income, population density, and coastal status are all significant controls. Income is positive with the largest coefficient which drives a large share of the raw ZHVI value, as would be expected (@fig-hedonic-income). A 1% change in median income results in `r hed_income_coef`% change in ZHVI (p \< 0.01). Housing markets are more than proportionally sensitive to differences in income that compound.

Specification A and B: We add the NRI controls with expected annual loss (log) and the community risk factor - both in its combined form and decomposed into resilience and social vulnerability scores. CRF is not significant in spec A, but the individual components are each significant in spec B. The proportionate ratio of social vulnerability to resilience in CRF obscures the relationship to housing market valuation. In a pattern that holds across our robustness checks (with a few exceptions mentioned later), log(EAL) remains negative and below 0.01 in magnitude while resilience is around -0.05 and SoVI is around -0.024. The negative resilience coefficient would suggest that a county raising its resilience score by one standard deviation would correspond to actually reducing property prices.

Specification C: the methodological regime attenuates the social vulnerability coefficient from `r hed_sovi_coef_B` to `r hed_sovi_coef_C`, but does not meaningfully change coefficients of any other feature.

Specification F: We test the resilience result by controlling for urbanness and ruralness using USDA’s Rural-Urban Continuum Codes (RUCC). Results are consistent with spec B showing that the resilience coefficient is not a product of resilience score valuing rural characteristics and rural markets having lower prices (@fig-hedonic-urban-rural).

```{r fig-hedonic-coeff, fig.cap="Hedonic regression coefficients on log(ZHVI)", out.width="100%"}
knitr::include_graphics(here::here("paper", "output", "hedonic", "hedonic_coefficient_plot.pdf"))
```

## Robustness Checks

The persistence of these specifications’ results is tested with multiple robustness checks. The main model, Spec B, is reconstructed without income and separately without SoVI to see if other coefficients are fragile to being conditioned on them. When income is removed, log(EAL) becomes significant at `r hed_eal_coef_E`\*\*\*, resilience becomes insignificant (`r hed_resl_coef_E`) and SoVI jumps to `r hed_sovi_coef_E`\*\*\*, confirming income’s dominance and the relative fragility of the others. Without SoVI there were no substantial changes in coefficients’ sign or magnitude.

Specs are attempted excluding coastal counties, using more conservative state clustered standard errors, and differentiating the pre and post-2023 time periods marking the SoVI measurement change (@tbl-robustness). All deliver results of a similar magnitude and sign with the exceptions of larger standard errors in the state-clustered model, and larger magnitude and significance level log(EAL) and resilience in the pre-2023 regime.

Going further, a collapsed panel cross-section using one observation per county per NRI vintage is constructed as a check against: attenuation in the income coefficient (a single 5-year income value) across the interpolated panel, or possible flaws in the interpolation method capturing within-county time variation. Each observation uses a mean ZHVI +/-6 month window from NRI release (with the exception of 2025 that uses a -6 to +3 month window due to availability of data) — this is the same cross-section shown as the panel-vs-cross-section comparison in the appendix (@fig-hedonic-panel-vs-xsec). The results of this more strict cross section hold coefficients of similar sign and magnitude. The only exceptions are the individual 2020 and 2021 results which have larger log(EAL) and resilience coefficients.

A minimum detectable effect (MDE) analysis (α = 0.05 (two-sided) and 80% power, MDE ≈ 2.8 × SE, computed separately for each coefficient from its own standard error in the cross-section) shows that log(EAL) falls below its detectable-effect threshold of 0.0149. This is not significant in our result, but small enough that we would likely not detect an effect even if real. Resilience and SoVI, by contrast, exceed their respective MDE thresholds of 0.024 and 0.01. See @fig-hedonic-mde.

This many tests warrant an eye on the multiple comparisons problem. In this case, we believe risk is mitigated by the facts that: the results are largely consistent in sign and magnitude, despite significant effects this is largely a null result being thoroughly examined, and results are interpreted conservatively in this study. 

## Sensitivity and Interpretation
If a 1% increase in expected annual loss reduces ZHVI by $β_{1}$ percent, then $β_{1}$ implies the market's effective capitalization rate on hazard losses. A common benchmark would be a 5% rough perpetuity discount on annual losses. Consider a county with the average US housing stock (~47,000 units) at the Zillow US median home value of \$368,720, carrying the 2025 median county-total expected annual loss of \$14.8M. That is ~\$315 of modeled annual loss per home. Full capitalization at a 5% perpetuity rate implies each home should lose \$315 / 0.05 = \$6,300 in value — about 1.7% of the home's value. In the log-log specification this corresponds to $β$* = −(315/368,720)/0.05 ≈ −0.017. The estimated $β_{log(EAL)}$ of −0.002 to −0.007 (statistically insignificant across primary specs) is roughly one-third to one-tenth of this reference and not distinguishable from zero; consistent with the market not measurably capitalizing modeled EAL at the county level. In this example, the corresponding log(EAL) coefficient would be above our minimum detectable effect threshold. One interesting note, the only models where EAL increased and was significant were the 2020 and 2021 specific snapshots, and the pre-2023 regime check: -.035\*\*\*, -.022\*\*\*, and -0.016\*\*\* respectively, all near or above this reference threshold and significant, which may suggest a more measurable relationship in that time period compared to the years following.

# Event Study Design

## Framework

For each county-month storm event, we measure the county's ZHVI trajectory relative to a counterfactual baseline of unaffected counties. Both the target county and each baseline county are indexed to 100 at the storm month (T=0), so deviations represent percentage-point changes in relative performance rather than dollar differences.

The monthly deviation at horizon $n$ is: $$\delta_{c,t+n} = Z_{c,t+n} - B_{c,t+n}$$

where $Z$ is the target county's indexed ZHVI and $B$ is the mean indexed ZHVI of the baseline counties. A positive deviation means the storm-affected county outperformed its baseline; negative means underperformance.

We summarize the post-storm trajectory as the Cumulative Impulse Response (CIR): $$\text{CIR}_{c,t} = \sum_{n=1}^{9} \delta_{c,t+n}$$ and measure the pre-storm trend as the annualized average deviation over `r PRE_EVENT_MONTHS` months prior to the event.

## Sample Construction

**Filters applied:**

- Storm events must have complete post-storm window within ZHVI coverage (through `r zhvi_date_max`)

- Target county must have ZHVI at T=0

- At least N clean baseline counties required (varies by method)

- AK, HI, PR excluded

- For tier analysis: only events with all three tiers present are retained

**Attrition and Covariate Balance:**

```{r setup-balance}
#| output: false
#| results: hide
#| message: false
source(here::here("paper", "R", "theme.R"))
source(here::here("paper", "R", "load_data.R"))
source(here::here("paper", "R", "balance.R"))

baselines <- list(
  level1   = load_baseline(BASELINE_LEVEL1_PATH, "First Ring (R1)"),
  level2   = load_baseline(BASELINE_LEVEL2_PATH, "Second Ring (R2)"),
  regional = load_baseline(BASELINE_REGIONAL_PATH, "Regional")
)

baselines$level1$path   <- BASELINE_LEVEL1_PATH
baselines$level2$path   <- BASELINE_LEVEL2_PATH
baselines$regional$path <- BASELINE_REGIONAL_PATH

storms <- read_csv(here::here("data", "processed", "storm_events.csv"),
                   col_types = cols(stcofips = col_character()),
                   show_col_types = FALSE)

balance <- run_balance(baselines, storms, here::here("paper", "output", "balance"))

# Baseline coverage stats
att <- balance$attrition_df
n_events_l1       <- format(att$covered_events[att$baseline == "First Ring (R1)"], big.mark = ",")
n_events_l2       <- format(att$covered_events[att$baseline == "Second Ring (R2)"], big.mark = ",")
n_events_regional <- format(att$covered_events[att$baseline == "Regional"], big.mark = ",")
n_counties_l1       <- format(att$covered_counties[att$baseline == "First Ring (R1)"], big.mark = ",")
n_counties_l2       <- format(att$covered_counties[att$baseline == "Second Ring (R2)"], big.mark = ",")
n_counties_regional <- format(att$covered_counties[att$baseline == "Regional"], big.mark = ",")
pct_survival_l1       <- round(att$covered_events[att$baseline == "First Ring (R1)"] / att$total_storms[1] * 100, 1)
pct_survival_l2       <- round(att$covered_events[att$baseline == "Second Ring (R2)"] / att$total_storms[1] * 100, 1)
pct_survival_regional <- round(att$covered_events[att$baseline == "Regional"] / att$total_storms[1] * 100, 1)
```

```{r tbl-balance-summary}
#| results: 'asis'
#| message: false
#| tbl-cap: "Covariate balance: mean difference (bias) and standard deviation (spread) of target minus baseline county characteristics per event."
#| tbl-pos: "H"
read_csv(here::here("paper", "output", "balance", "balance_summary.csv"),
         show_col_types = FALSE) |>
  transmute(
    Baseline = baseline,
    N        = scales::comma(n_events),
    `Mean`   = mean_zhvi,
    `SD`     = sd_zhvi,
    `Mean `  = scales::comma(mean_income),
    `SD `    = scales::comma(sd_income),
    `Mean  ` = mean_resl,
    `SD  `   = sd_resl,
    `Mean   `= mean_eal,
    `SD   `  = sd_eal
  ) |>
  kableExtra::kbl(
    booktabs = TRUE,
    longtable = FALSE,
    col.names = c("Baseline", "N", "Mean Diff", "SD Diff", "Mean Diff", "SD Diff", "Mean Diff", "SD Diff", "Mean Diff", "SD Diff"),
    align = c("l", "r", rep("r", 8))
  ) |>
  kableExtra::add_header_above(c(" " = 2, "ZHVI (log)" = 2, "Income ($)" = 2, "Resilience" = 2, "EAL (log)" = 2)) |>
  kableExtra::kable_styling(latex_options = "scale_down")
```

Three counterfactual baselines are constructed as the equal-weighted mean ZHVI of a set of unaffected counties. Baseline counties must have 0 reported NOAA storm events in the pre and post storm timeframe to create an unaffected index.

First Ring (R1) neighboring counties are the group of counties physically connected to the target county. This represents the closest counterfactual to the storm-affected county, but it absorbs the highest level of spillover effect. R1 represents `r n_events_l1` events across `r n_counties_l1` counties, `r pct_survival_l1`% survival rate.

Second Ring (R2) counties are the adjacent neighbors of the R1 counties, exclusive of any R1 counties. These are isolated from the target county by 1 neighbor, so the physical separation reduces the spillover effect at the cost of greater heterogeneity from the target. R2 represents `r n_events_l2` events across `r n_counties_l2` counties, `r pct_survival_l2`% survival rate.

Regional baseline is constructed from all counties in the local climatological region as defined by Karl & Koss (1984) that were unaffected by NOAA storm events in the pre and post measurement periods. Regional baseline represents `r n_events_regional` events across `r n_counties_regional` counties, `r pct_survival_regional`% survival rate.

R2 and regional baselines must have at least 2 unaffected counties. The first ring baseline may have 1 or more unaffected counties (see @tbl-balance-summary and @fig-balance for per-event covariate balance across the three baselines).

# Event Study Results

## Trajectories

```{r setup-es}
#| output: false
#| results: hide
#| message: false
source(here::here("paper", "R", "event_study.R"))
es <- run_event_study(baselines, here::here("paper", "output", "event_study"))

# Pre-storm significance check (L2, mid tier)
pre_storm_check <- baselines$level2$monthly_dev |>
  filter(tier == "mid", month_t %in% c(-3, -2, -1)) |>
  group_by(month_t) |>
  summarise(
    mean_dev = mean(deviation, na.rm = TRUE),
    se_dev   = sd(deviation, na.rm = TRUE) / sqrt(n()),
    p_value  = 2 * pt(-abs(mean_dev / se_dev), df = n() - 1),
    .groups  = "drop"
  )

pre_t1_p <- round(pre_storm_check$p_value[pre_storm_check$month_t == -1], 3)
pre_t2_p <- round(pre_storm_check$p_value[pre_storm_check$month_t == -2], 3)
pre_t3_p <- round(pre_storm_check$p_value[pre_storm_check$month_t == -3], 3)
pre_t1_dev <- round(pre_storm_check$mean_dev[pre_storm_check$month_t == -1], 3)
```

```{r fig-es-mid, fig.cap="Post-storm ZHVI trajectory for Mid tier housing by baseline method. R1 (first ring) shows the smallest deviation, Regional the largest.", out.width="100%"}
knitr::include_graphics(here::here("paper", "output", "event_study", "fig_es_mid.pdf"))
```

All three baselines show post-storm appreciation relative to baseline counties across all tiers (Bottom and Top tier trajectories, shown in @fig-es-bottom and @fig-es-top, follow the same pattern). The magnitude of measured deviation depends on baseline choice. R1 shows the smallest deviation, consistent with spillover contamination of adjacent counties. R2 and Regional show larger deviations. Regional and R2 baselines diverge significantly from zero by T+4 (95% CI).

Pre-storm deviation of `r pre_t1_dev` at T-1 is significant for R2 Mid tier (p = `r pre_t1_p`), with T-2 borderline (p = `r pre_t2_p`) and T-3 not significant (p = `r pre_t3_p`). The direction is negative, as target counties slightly underperform their baseline in the lead-up to storm events. This pre-storm deviation is statistically significant, so we adjust for the pre-trend period in the regression analysis.

## Regression

Each model regresses the Cumulative Impulse Response (CIR) on pre-storm trend and a block of controls that grows across five nested specifications (@tbl-buildup). All specifications include month-year fixed effects, with standard errors two-way clustered by county and month-year .

- Spec 1: Pre-trend alone
- Spec 2: + coastal status, log income, log population density
- Spec 3: + log storm damage
- Spec 4: + log NRI risk value
- Spec 5: + log EAL, resilience, and SoVI in place of the composite risk value .

```{r setup-reg}
#| output: false
#| results: hide
#| message: false
source(here::here("paper", "R", "regression.R"))
reg <- run_regression(baselines, here::here("paper", "output", "regression"))

# ---- Regression inline values ----
# Buildup (L2 mid)
m1_coefs <- coef(reg$models_buildup[["M1: Baseline"]])
m5_coefs <- coef(reg$models_buildup[["M5: + Components"]])
m1_r2w <- round(as.numeric(fitstat(reg$models_buildup[["M1: Baseline"]], "wr2")), 3)
m5_r2w <- round(as.numeric(fitstat(reg$models_buildup[[length(reg$models_buildup)]], "wr2")), 3)

pre_trend_coef    <- round(m1_coefs["pre_trend_annual"], 2)
coastal_coef      <- sprintf("%.2f", m5_coefs["coastal"])
coastal_se        <- round(se(reg$models_buildup[[length(reg$models_buildup)]])["coastal"], 3)

# Baseline sensitivity
bs <- reg$baseline_models
pre_trend_regional <- round(coef(bs[["Regional"]])["pre_trend_annual"], 2)
pre_trend_l2       <- round(coef(bs[["Second Ring (R2)"]])["pre_trend_annual"], 2)
pre_trend_l1       <- round(coef(bs[["First Ring (R1)"]])["pre_trend_annual"], 2)
coastal_l2         <- round(coef(bs[["Second Ring (R2)"]])["coastal"], 2)
coastal_regional   <- round(coef(bs[["Regional"]])["coastal"], 2)
coastal_l1         <- round(coef(bs[["First Ring (R1)"]])["coastal"], 2)
risk_l1            <- sprintf("%.2f", coef(bs[["First Ring (R1)"]])["log_risk_value"])
n_obs_l1           <- nobs(bs[["First Ring (R1)"]])
r2w_regional <- round(as.numeric(fitstat(bs[["Regional"]], "wr2")) * 100, 1)
r2w_l2       <- round(as.numeric(fitstat(bs[["Second Ring (R2)"]], "wr2")) * 100, 1)
r2w_l1       <- round(as.numeric(fitstat(bs[["First Ring (R1)"]], "wr2")) * 100, 1)

# Tier comparison
tc <- reg$tier_models
damage_bottom      <- round(coef(tc[["Bottom"]])["log_damage"], 2)
coastal_bottom     <- round(coef(tc[["Bottom"]])["coastal"], 2)
coastal_mid        <- round(coef(tc[["Mid"]])["coastal"], 2)
coastal_top        <- round(coef(tc[["Top"]])["coastal"], 3)
eal_top            <- round(coef(tc[["Top"]])["log_eal_valt"], 2)
r2w_bottom   <- round(as.numeric(fitstat(tc[["Bottom"]], "wr2")) * 100, 1)
r2w_mid_tier <- round(as.numeric(fitstat(tc[["Mid"]], "wr2")) * 100, 1)
r2w_top      <- round(as.numeric(fitstat(tc[["Top"]], "wr2")) * 100, 1)

pre_trend_mid    <- round(coef(tc[["Mid"]])["pre_trend_annual"], 2)
pre_trend_bottom <- round(coef(tc[["Bottom"]])["pre_trend_annual"], 2)
pre_trend_top    <- round(coef(tc[["Top"]])["pre_trend_annual"], 2)
```

```{r tbl-buildup}
#| results: 'asis'
#| tbl-cap: "Model Buildup: Mid Tier, Second Ring (R2) Baseline"
writeLines(readLines(here::here("paper", "output", "regression", "table_buildup.tex")))
```

### Model Buildup (Mid Tier, R2)

Pre-storm trend is the only predictor significant in every specification (`r pre_trend_coef`). Coastal becomes significant in the full specification, M5 (`r coastal_coef`), separating the specific effect of coastal location from NRI counterparts. Log damage, log income, log population density, NRI risk value, expected annual loss, resilience, and social vulnerability are all insignificant. Within R² is essentially flat from M1 to M5 (`r m1_r2w*100`% to `r m5_r2w*100`%). Storm and NRI variables add negligible explanatory power beyond pre-trend. The pre-trend coefficient implies strong mean reversion. Counties underperforming before the storm outperform after, regardless of storm characteristics.

### Baseline Sensitivity (Mid Tier, Preferred Spec)

Baseline sensitivity results appear in @tbl-baseline. Pre-trend coefficient varies by baseline: Regional (`r pre_trend_regional`) \> R2 (`r pre_trend_l2`) \> R1 (`r pre_trend_l1`), all significant at 1%. Coastal is significant only on R2 (`r coastal_l2`\*\*). Regional shows same direction (`r coastal_regional`) but wider SE. R1 shows no effect (`r coastal_l1`). Within R² rises as the baseline moves farther from the target, from `r r2w_l1`% (R1) to `r r2w_regional`% (Regional). The pre-trend carries more explanatory power against more distant counterfactuals, so the baseline choice itself shifts the R². No other variable reaches significance at the 5% level. The null results on NRI risk value and storm characteristics are robust to baseline choices.

### Tier Comparison (R2, Preferred Spec)

ZHVI tier comparison results appear in @tbl-tier. Pre-trend is significant and similar across all tiers (`r pre_trend_top` to `r pre_trend_mid`\*\*\*). Coastal is significant at 5% on Mid (`r coastal_mid`\*\*), marginally significant on Bottom (`r coastal_bottom`\*), and insignificant on Top (`r coastal_top`). Log damage is marginally significant on the Bottom tier only (`r damage_bottom`\*). Damage is associated with price depreciation in the lowest market segment. The NRI risk coefficient varies across tiers, but the null effect is robust across market segments. NRI does not capture tier-specific vulnerability. Within R² is highest on Bottom tier (`r r2w_bottom`%) and lowest on Top (`r r2w_top`%). Storm characteristics explain slightly more variance in financially vulnerable markets.

## Temporal Effects of Damage Post-Storm

The damage coefficient in the R2 baseline for the Bottom market tier approaches but does not achieve significance when measured as cumulative impulse response. We investigate the temporal effect of damage to understand if it is significant for certain timeframes post-storm event using a local projection approach.

At each post-storm horizon, each ZHVI deviation ($\delta_{c,t+n}$) is regressed separately on:

- Pre-storm trend
- Coastal status
- Log income
- Log population density
- Log storm damage
- Log NRI risk value

with month-year fixed effects and standard errors two-way clustered by county and month-year.

```{r setup-lp}
#| output: false
#| results: hide
#| message: false
source(here::here("paper", "R", "lp_did.R"))
lp <- run_lp(baselines, here::here("paper", "output", "lp"))

# ---- LP inline values ----
# Bottom tier damage coefficient range (L2)
lp_bottom <- lp$lp_by_tier |> filter(tier == "Bottom", horizon > 0)
lp_bottom_min <- round(min(lp_bottom$estimate, na.rm = TRUE), 3)
lp_bottom_max <- round(max(lp_bottom$estimate, na.rm = TRUE), 3)
lp_bottom_t5  <- round(lp_bottom$estimate[lp_bottom$horizon == 5], 3)
lp_bottom_t9  <- round(lp_bottom$estimate[lp_bottom$horizon == 9], 3)

# Placebo check — max absolute coefficient pre-storm across all tiers
lp_placebo <- lp$lp_by_tier |> filter(horizon < 0)
lp_placebo_max <- round(max(abs(lp_placebo$estimate), na.rm = TRUE), 3)
```

### Dynamic damage by baseline (Bottom tier):

R2 baseline shows a significant negative damage signal post-storm with significance at T+2 through T+5. R1 baseline is flat, consistent with spillover contamination. Regional baseline is noisier and more reflective of covariate imbalance than meaningful effect. The pre-storm period is uncorrelated with damage.

```{r  fig-lp-baseline, fig.cap="Dynamic effect of log property damage on ZHVI deviation by baseline method. Bottom tier only. Progressive attenuation from R2 to R1 is consistent with spillover contamination of adjacent baselines.", out.width="100%"}
knitr::include_graphics(here::here("paper", "output", "lp", "fig_lp_baseline.pdf"))
```

### Damage by tier (R2 baseline):

Placebo region (T-3 to T-1) is flat for all tiers (maximum absolute coefficient `r lp_placebo_max`). The tier projection shows that much of the effect is focused in the Bottom market tier, with coefficients ranging from `r lp_bottom_min` to `r lp_bottom_max` across post-storm horizons. Mid and Top tier damage coefficients are indistinguishable from zero at all horizons. Effects show partial recovery at later horizons (T+9 coefficient = `r lp_bottom_t9` vs trough of `r lp_bottom_min`).

```{r  fig-lp-tier, fig.cap="Dynamic effect of log property damage on ZHVI deviation by market tier. Second Ring (R2) baseline. Red shading = placebo region (T-3 to T-1). Blue shading = post-storm window.", out.width="100%"}
knitr::include_graphics(here::here("paper", "output", "lp", "fig_lp_tier.pdf"))
```

# Discussion

## Income + Hedonic Results

The hedonic regression shows income as the dominant predictor of the absolute ZHVI level, and this holds across time periods and specifications. During the storm-recovery window (T+1 to T+9), however, income does not significantly predict the relative dynamics, the percentage-point deviation of the storm-affected county from its baseline. Income predicts typical home values, but not the cumulative impulse response, which captures both the magnitude and the persistence of that deviation.

Stratifying the market into Bottom, Mid, and Top ZHVI tiers leaves income insignificant in every tier. Income is measured at the county level, while the tiers separate segments of the housing market within a county, so we cannot observe how income varies across tiers. The Bottom tier represents lower-value homes, which would be the most likely to register the valuation impact of severe damage, underinsurance, or forced sales - though ZHVI lacks the resolution to confirm this mechanism. Either way, a home's value tier is distinct from, and cannot be mapped to, the income of its owner.


## National Risk Index as a summary metric

NRI variables are insignificant as predictors of post-storm CIR. When tested against the event study, many of the significant factors of the hedonic regression turn to noise. The model has sufficient sample to detect other effects (coastal, damage), so we believe these are genuine null results. Counties with high NRI scores are indistinguishable from counties with low NRI. NRI may reflect long-term or broad-based risk, but when examined through the specific events captured in NOAA storm data, the NRI and its components individually offer no explanatory power.

## ZHVI as a measurement

One of the caveats to the findings on income and NRI is that storms can have targeted impacts that do not get fully captured in aggregated Zillow indices. A more clear picture of specific storm impacts could be seen with transaction level data. This is noted as an area for future investigation if a data source becomes available.

## Challenges of NOAA data

Storm data features high spillover rate without clear boundaries. This is evidenced by the differences in First Ring (R1) and Second Ring (R2) baselines. We recognize that our qualification of a 'clean' baseline that has no recorded events does not necessarily mean that the baseline county did not experience weather. Additionally, reporting of events and damage levels is voluntary and reports can reflect the resources available for reporting rather than the actual levels of storms.

## Natural experiment design

The natural experiment design reflects the challenges of the storm and ZHVI data outlined above. R2 is the preferred baseline because it buffers spillover without introducing regional heterogeneity. However, with so many events and factors that cross county boundaries, there is no one correct version of a baseline for comparison. Selecting an appropriate baseline is a balance of decontaminating the spillover and accurately capturing the local dynamics.

### Pre-trend

The dominant signal across all event study analyses is pre-existing momentum, not storm effects. In all cases the effect of the `r PRE_EVENT_MONTHS` months of pre-trend difference on the post-event performance is robust and significant across different baselines and market tiers. Counties appreciate on average post-storm, but that appreciation is a rebound: the pre-trend coefficient is negative, indicating a fluctuation in market direction that consistently happens around the storm cycle.

### Coastal areas

The difference-in-differences design has the power to detect a coastal effect that is significant on R2 but not on R1. This finding is consistent with the high level of spillover suspected with R1 neighbors, and supports R2 as the preferred baseline. Coastal penalty is strongest on Bottom and Mid, absent on Top. Top market tier exhibits economic stability against storm events as amenity value protects high-end coastal property.

### Damage significant but limited

The damage effect is significant, but only for the Bottom market tier, which is the most financially constrained market segment where forced sales, deferred repairs, and underinsurance are most likely to appear. In the cumulative impulse response, the effect only reached the 10% level of significance for the Bottom tier. The local projections analysis refines that finding through its timing dynamics: the damage effect is most significant in the T+2 to T+5 timeframe. The Top tier exhibits no damage effect which reinforces the finding that the Top tier avoids the coastal penalty. High-value properties retain their amenity value despite storm-specific shocks.

# Conclusions

The expectation might be that property prices reflect risk by penalizing riskiness and rewarding resilience characteristics. We do not find evidence in this investigation of property prices accounting for NRI factors. The descriptive hedonic cross-section analysis and a storm-based natural experiment both find FEMA NRI and its climate-risk components to be essentially null predictors of home values. Because the designs analyze the ZHVI with different methodology, the agreement indicates the null reflects the data rather than a single specification choice.

This result could be explained by a number of scenarios, among them, A) property pricing is determined by an array of factors, the bulk of which outweigh any climate risk or resilience as measured by NRI, B) NRI measures a number of factors only some of which matter to pricing, C) NRI is a poor measure of climate related risk or resilience as related to pricing, D) climate risk is ignored by property markets resulting in inefficiency. 

The absolute level of county home values is dominated by income, followed by amenity (coastal location) and population density. These are the expected structural drivers of housing value, and their prominence is consistent with prior hedonic work.

In the storm quasi-experiment, the dominant signal is pre-existing price momentum, not a hazard response. Post-storm trajectories are governed by mean reversion based on the pre-storm trend relative to baseline. NRI factors (EAL, resilience, social vulnerability) do not explain the post-storm housing market response. Property damage is only marginally associated with depreciation in the Bottom market tier over a limited timeframe post-event. The Top tier of the market is resistant to valuation impacts of storm damages and coastal risks. 

## Limitations

The hedonic regression measures correlation conditional on observables. The county-level coastal dummy and ACS controls do not fully purge amenity bias (people pay more to live near oceans regardless of climate risk). The hedonic coefficient is therefore a lower bound on the true risk discount in absolute terms - the market may discount risk more than we measure, but the amenity premium is netting against it.

The SoVI methodology break in March 2023 means the pooled-sample SoVI coefficient mixes two different measurements. The regime-interaction term in Spec C and the stratified robustness checks test whether this matters in practice. Possibilities include market changes over the time period, differences in measurement (and quality of operationalization), e.g. if the SoVI estimate started explaining more and absorbed some explanatory power of EAL and Resilience. Coefficients on log(EAL), resilience, and SoVI hold sign and comparable magnitude moving from the full county-month panel (Spec C) to the vintage-collapsed cross-section (xs_B), which is some reassurance that the pooled estimates are not an artifact of the SoVI regime break, though it does not rule it out (@fig-hedonic-panel-vs-xsec).

ZHVI is an index, not specific market transactions, so we cannot observe the changes in individual home values that aggregate into the index. The effects that we observe in the index are averaged across the entire market tier, so small localized effects are dampened. There is no ability to track individual homes across market tiers, so any storm effects that cause a home to fall out of Mid and Top tiers into the Bottom, or that raise the value of homes post-storm, are attenuated. 

NOAA damage reporting is inconsistent across counties. Reporting is voluntary, so different locales will have different reporting standards. Damage assessments are incomplete, so we do not have a complete view of how much damage is actually caused for each episode. 

Spillover effects are inherent and unavoidable in weather-related analysis. Storms do not behave according to county boundaries. While we condition baseline counties to have 0 recorded storm events during a `r PRE_EVENT_MONTHS + POST_EVENT_MONTHS` month window, we do not know what level of severe weather actually materialized during that time frame. 

To manage spillover effects, we had to exclude a large number of the storm and county observations from the study - less than 5% of counties survived the filters. While this produces a framework to help measure storm effects, this measurement does not generalize to all real-world counties. Counties with the greatest level of storm effects are likely to exist near other counties that also have high levels of storm effects. 

The event study does not inform about the long-term effects of individual storms or storm trends due to climate change. We measure the housing market for `r POST_EVENT_MONTHS` months after a specific event, so our analysis is limited to the window of time after discrete events. 

# References

Bakkensen, L.A. & Barrage, L. (2017). Flood risk belief heterogeneity and coastal home price dynamics: Going under water? NBER Working Paper No. 23854. <https://www.nber.org/papers/w23854>

Baldauf, M., Garlappi, L., Yannelis, C., & Scheinkman, J. (2020). Does climate change affect real estate prices? Only if you believe in it. *The Review of Financial Studies*, 33(3), 1256--1295. <https://doi.org/10.1093/rfs/hhz073>

Bernstein, A., Gustafson, M.T., & Lewis, R. (2019). Disaster on the horizon: The price effect of sea level rise. *Journal of Financial Economics*, 134(2), 253--272. <https://doi.org/10.1016/j.jfineco.2019.03.013>

Büchler, S., Palacios, J., Sun, X., & Zheng, S. (2024). Adapting to risk? How investor beliefs shape climate adaptation in real estate portfolios. RERI Working Paper. <https://www.reri.org/research/files/buchler_palacios_sun_zheng_paper.pdf>

Congressional Budget Office. (2023, November). Flood damage and federally backed mortgages in a changing climate. <https://www.cbo.gov/publication/59753>

Contat, J. (2024). When climate meets real estate: A survey of the literature. *Real Estate Economics*, 52, 618--659.

Coren, M. (2024, November 5). Everyone's ignoring these investors' warnings on climate risk. You shouldn't. *Washington Post*. <https://www.washingtonpost.com/climate-environment/2024/11/05/real-estate-investor-climate-change-risks/>

Coren, M., Ahmed, N., & Crowe, K. (2024, November 20). See if your city is poised to bounce back from the next climate disaster. *Washington Post*. <https://www.washingtonpost.com/climate-environment/interactive/2024/climate-risk-resilience-factors-us-cities/>

Dube, A., Girardi, D., Jordà, Ò., & Taylor, A.M. (2025). A local projections approach to difference-in-differences. *Journal of Applied Econometrics*, 40(7). <https://doi.org/10.1002/jae.70000>

Federal Housing Finance Agency. (2024). Estimating the impact of Hurricanes Helene and Milton on single-family mortgages. <https://www.fhfa.gov/blog/insights/estimating-the-impact-of-hurricanes-helene-and-milton-on-single-family-mortgages>

Gourevitch, J.D., Kousky, C., et al. (2023). Unpriced climate risk and the potential consequences of overvaluation in US housing markets. *Nature Climate Change*, 13. <https://www.nature.com/articles/s41558-023-01594-8>

Jordà, Ò. (2005). Estimation and inference of impulse responses by local projections. *American Economic Review*, 95(1), 161--182.

Karl, T.R. & Koss, W.J. (1984). *Regional and National Monthly, Seasonal and Annual Temperature Weighted by Area, 1895--1983.* Historical Climatology Series 4-3. National Climatic Data Center, Asheville, NC.

Ma, L. & Yildirim, Y. (2023). High temperature, climate change and real estate prices. Preliminary manuscript, Baruch College--CUNY. <https://www.haas.berkeley.edu/wp-content/uploads/High-Temperature-Climate-Change-and-Real-Estate-Prices-Li-Ma.pdf>

Parshley, L. (2023, October 10). As climate risks mount, the insurance safety net is collapsing. *Grist*. <https://grist.org/economics/as-climate-risks-mount-the-insurance-safety-net-is-collapsing/>

Smith, A. (2025, January 10). 2024: An active year of U.S. billion-dollar weather and climate disasters. *NOAA*. <https://www.climate.gov/news-features/blogs/beyond-data/2024-active-year-us-billion-dollar-weather-and-climate-disasters>

U.S. Department of Agriculture, Economic Research Service. (2023). Rural-Urban Continuum Codes. <https://www.ers.usda.gov/data-products/rural-urban-continuum-codes>

Wowk, C. (2021). Burning down the house: How inadequate climate risk disclosures and information asymmetries threaten to disrupt the U.S. mortgage market. Duke University Economics Department. <https://econ.duke.edu/dfe/climate-risk/2021/02/burning-down-house-how-inadequate-climate-risk-disclosures-and-information>

Zivin, J.G., Liao, Y., & Panassié, Y. (2023). How hurricanes sweep up housing markets: Evidence from Florida. *Journal of Environmental Economics and Management*, 118.

\newpage
# Appendix
```{r fig-hedonic-income, fig.cap="(log(EAL), resilience, SoVI, coastal) estimated with and without controlling for income.", out.width="100%", fig.pos="H"}
knitr::include_graphics(here::here("paper", "output", "hedonic", "hedonic_income_comparison.pdf"))
```
```{r fig-hedonic-urban-rural, fig.cap="Resilience, income, and home values across the urban-rural continuum. All series indexed to RUCC 1 (large metro) = 100.", out.width="100%", fig.pos="H"}
knitr::include_graphics(here::here("paper", "output", "hedonic", "hedonic_urban_rural.pdf"))
```
```{r fig-hedonic-mde, fig.cap="Minimum Detectable Effect vs. estimated coefficient magnitude for log(EAL), resilience, and SoVI (grey band = 80-90% power MDE).", out.width="100%", fig.pos="H"}
knitr::include_graphics(here::here("paper", "output", "hedonic", "hedonic_mde_plot.pdf"))
```
```{r fig-hedonic-panel-vs-xsec, fig.cap="Panel hedonic vs. vintage-collapsed cross-section,full county-month panel (Spec C) and the vintage-collapsed cross-section (xs_B).", out.width="100%", fig.pos="H"}
knitr::include_graphics(here::here("paper", "output", "hedonic", "hedonic_panel_vs_xsec_plot.pdf"))
```
```{r tbl-robustness}
#| results: 'asis'
#| tbl-cap: "Hedonic robustness checks against Spec B: inland-only sample, state-clustered standard errors, and CDC (2023+) vs HVRI (pre-2023) SoVI regimes."
#| tbl-pos: "H"
writeLines(readLines(here::here("paper", "output", "regression", "table_robustness.tex")))
```
```{r tbl-hedonic-xsec}
#| results: 'asis'
#| tbl-cap: "Hedonic Cross Section Comparison"
#| tbl-pos: "H"
writeLines(readLines(here::here("paper", "output", "regression", "table_hedonic_zhvi_full_window_check.tex")))
```
```{r fig-balance, fig.cap="Per-event covariate balance: target minus baseline mean. Red dashed line indicates perfect balance (zero difference). Rows share x-axes for visual comparison across baseline methods.", out.width="100%", fig.pos="H"}
knitr::include_graphics(here::here("paper", "output", "balance", "fig_balance.pdf"))
```
```{r fig-es-bottom, fig.cap="Post-storm ZHVI trajectory for Bottom tier housing by baseline method. Wider confidence intervals reflect thinner transaction volume.", out.width="100%", fig.pos="H"}
knitr::include_graphics(here::here("paper", "output", "event_study", "fig_es_bottom.pdf"))
```
```{r fig-es-top, fig.cap="Post-storm ZHVI trajectory for Top tier housing by baseline method.", out.width="100%", fig.pos="H"}
knitr::include_graphics(here::here("paper", "output", "event_study", "fig_es_top.pdf"))
```
```{r tbl-baseline}
#| results: 'asis'
#| tbl-cap: "Baseline Sensitivity: Mid Tier, Full NRI Specification"
#| tbl-pos: "H"
writeLines(readLines(here::here("paper", "output", "regression", "table_baseline_sensitivity.tex")))
```
```{r tbl-tier}
#| results: 'asis'
#| tbl-cap: "Tier Comparison: Second Ring (R2) Baseline, Full NRI Specification"
#| tbl-pos: "H"
writeLines(readLines(here::here("paper", "output", "regression", "table_tier_comparison.tex")))
```